%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%	
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%	
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,5pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.4\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{3pt}{3pt}
\titlespacing{\subsection}{0pt}{3.5pt}{3pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Alfredo Gonz\'alez-Espinoza, PhD} \\[6pt]
\href{https://github.com/spiralizing}{\raisebox{-0.05\height}\faGithub\ spiralizing} \ $|$ \ 
\href{https://linkedin.com/in/agonzaleze}{\raisebox{-0.05\height}\faLinkedin\ agonzaleze} \ $|$ \ 
\href{https://spiralizing.github.io/}{\raisebox{-0.05\height}\faGlobe \ spiralizing.github.io} \ 
\\
\href{mailto:spiralizing@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ spiralizing@gmail.com} \ $|$ \ 
\href{tel:+14847588636}{\raisebox{-0.05\height}\faMobile \ (+1) 484 758 8636} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Interests/ Keywords/ Summary
\section{Summary}
Data Scientist with a research background in Chemistry, Physics and Data Science. Demonstrated expertise in solving complex interdisciplinary problems and delivering innovative solutions. Passionate about data-oriented research and data-driven product development that contribute to generating a positive impact in society by solving real world problems. 
%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Strengths \& Skills}
Creative thinker driven by intellectual curiosity and the excitement of exploring new challenges. Highly motivated to learn new skills and topics, and focused on continuous growth. Exceptional project management abilities and effective communication skills across diverse teams. Proficient in translating technical concepts into actionable insights for both technical and non-technical audiences. Inclusive and collaborative team player, attentive listener who values feedback, reflection, and self awareness.  
\\
{\bf Methodological expertise:}\\
Complex Systems, Time Series Analysis, Stochastic Simulations, Network/Graph Theory, Information Theory, Hypothesis Testing, Machine Learning, Statistical Inference, Natural Language Processing.
\\
{\bf Technical Skills:}\\
Languages: Julia, Python (Pandas, Numpy, Matplotlib, PySpark, Keras, TensorFlow, PyTorch, Scikit-learn, NLTK, spaCy, scipy, Flask). Other: R (familiar), Linux, Bash, LaTeX, Git, SQL, Jupyter notebook, Pluto notebook, MLOps (CI/CD).
%Experience
\section{Work Experience}
\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Postdoctoral Researcher}, University of Pennsylvania, PA, USA. & \hfill 2019 - 2022 \\[3.75pt]
\multicolumn{2}{@{}X@{}}{I led a research project in the mathematical biology group, focusing on quantifying the evolution of musical features and innovation in musical scores. Relevant work included: Data collection, cleaning and processing from diverse sources and in variable formats. I developed mathematical and probabilistic models, implemented computational algorithms and experiments for hypothesis testing. I also built and maintained data infrastructure and git repositories, develop quantitative research methods to analyze results. I wrote software documentation and research manuscripts for publication. Results featured in the prestigious journal Scientific American.
}
\end{tabularx}
\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Postdoctoral Researcher}, National Institute of Genomic Medicine, M\'exico. & \hfill 2018 - 2019 \\[3.75pt]
\multicolumn{2}{@{}X@{}}{Developed the methodology and analysis to quantify different types of malignancy in breast cancer, and contributed to potential treatments. Relevant work included: collaborating with an interdisciplinary team on projects, developing a novel machine learning algorithm to identify communities of statistically dependent genes. I performed advanced statistical analysis and quantifies genomic features using information measures. I mentored PhD students in their research projects, present results weekly to PI and managers. Wrote software documentation and research manuscript for publication.
}
\end{tabularx}
%Projects
\subsection*{Other Experience/Projects}
\begin{tabularx}{\linewidth}{ @{}l r@{} }
%\textbf{Miscellaneous} (2010 - Present) & \hfill  \\[3.75pt]
\multicolumn{2}{@{}X@{}}{I have a large array of diverse projects I have pursued in academic and non-academic environments. Most projects are data-oriented. A sample of these are listed here:
\begin{itemize}
    %\item Ab-Initio Molecular potential for Hydroxilamine (Monte Carlo, Regression, Molecular mechanics)
    %\item Pattern formation (2-D,3-D stochastic models, cellular automata, differential equations)
    %\item Bike sharing system, Mexico city (characterizing system usage with network/graph theory)
    \item Analyzed high-resolution spatio-temporal tracking data for a professional soccer team in Mexico
    \item Built and analyzed knowledge graphs of news articles using NLP and semantic graph techniques
    \item Developed an LSTM model for sentiment analysis of tweets in Spanish
    %\item Rank-frequency distribution analysis and stochastic modeling in written language (NLP).
    \item VADER sentiment analysis and topic modeling to characterize pop music
    %\item Inferring game strategies for online Diplomacy. (probabilistic and time series approach)
    %\item Estimating molecular energies. (linear regression)
    %\item Developed predictive models for wine properties and quality using ANN (regression analysis)
\end{itemize}
} 
\end{tabularx}
%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}	
2014 - 2018 & PhD in Science (Physics) \textbf{Universidad Autónoma del Estado de Morelos, M\'exico}  \\
            & \em{Graduated with honors} \\
2011 - 2014 & Master of Science (Physics) \textbf{Universidad Autónoma del Estado de Morelos} \\ 

2005 - 2011 & Bachelor of Science (Chemistry) \textbf{Universidad Autónoma del Estado de Morelos} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------
\section{Awards \& Selected Publications}
National scholarship for graduate studies (PhD) fully funded by CoNaCyT \\ 
National scholarship for graduate studies (Master degree) fully funded by CoNaCyT \\
\textbf{Alfredo González-Espinoza}, Gustavo Martínez-Mekler, and Lucas Lacasa. (2020) Arrow of
time across five centuries of classical music.  \textit{Phys. Rev. Research}, 2:033166.
\section{Interests \& Activities}
Amateur cellist/musician, Photography, Soccer, Videogames, Continuos learning, Science Communication, Neuroscience, Urban planning
\vfill
%\center{\footnotesize Last updated: \today}

\end{document}
